Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-20 paper.qmd
Added b1 Vs m plot for the diagnostics

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = bin1, 
                         y = MSE)) + 
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) + 
  geom_vline(xintercept = 11, linetype="solid",
             color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 9, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 13, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  scale_x_continuous(breaks = 5:19) +
  labs(x = expression(b[1]), y = "MSE") +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))
```

@@

cell_count_scurve + mse_scurve_b +  
mse_scurve_lwd + 
distance_hist + plot_layout(ncol=2)
```

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = bin1, 
                         y = MSE)) + 
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) + 
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_x_continuous(breaks = 5:19) +
  labs(x = expression(b[1]), y = "MSE") +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))

b1_m_scurve <- ggplot(error_scurve, 
                     aes(x = bin1, 
                         y = b_non_empty)) + 
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) + 
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_x_continuous(breaks = 5:19) +
  labs(x = expression(b[1]), y = expression(m)) +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))
```

@@

b1_m_scurve + mse_scurve_b +  
mse_scurve_lwd + 
distance_hist + plot_layout(ncol=2)
```
